A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 main.tex
Updates from Overleaf

\cm{I will cut this accuracy subsection. In exchange, I will conduct a log-rank test}
\subsection{Accuracy}
Fig.~\ref{fig:acc} shows the advernsarial and benign accuracies for all datasets and hardware. It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware though CIFAR10 has worse benign performance and CIFAR100 has substantially worse adversarial performance. For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g. the accuracy we would expect on random noise), demonstrating the efficacy of the attack outlined in Sec.~\ref{optimisation}.

@@

\subsection{Time}
Fig.~\ref{fig:time} reveals the training time. Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference. This should be no surprise since the less-capable hardware is meant to be used exclusively for inference. Additionally, the attack time increases with both the training and prediction times across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth,trim={100pt 0 100pt 0},clip]{plots/combined/cost.pdf}
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure}

>>>>

\subsection{Accuracy}
Fig.~\ref{fig:acc} shows the adversarial (right) and benign (left) accuracies for all datasets and hardware. It demonstrates little to no change in accuracy or adversarial accuracy, regardless of hardware though CIFAR10 has worse benign performance and CIFAR100 has substantially worse adversarial performance. For all three datasets, the adversarial accuracy becomes the reciprocal of the number of classes (e.g. the accuracy we would expect on random noise), demonstrating the efficacy of the attack outlined in Sec.~\ref{optimisation}.

@@

\subsection{Time}
Fig.~\ref{fig:time} reveals the training time, inference time, and attack generation time across all datasets and models. Slower hardware (see Memory Bandwidth in Tab.~\ref{tab:hardware}) is only a few milliseconds slower, so this is unlikely to be noticeable to an end-user during inference. This should be no surprise since the less-capable hardware is meant to be used exclusively for inference. Additionally, the attack time (right sub-figure) increases with both the training (left) and prediction times (center) across hardware and datasets --- an expected result since this is driven by the number of samples and the inference time (see Eq.~\ref{attack_time}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/time.pdf}
    \caption{Training, Prediction, and Attack times across datasets and hardware.}
    \label{fig:time}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/power.pdf}
    \caption{Training, Prediction, and Attack Power Consumption Across Datasets and Hardware}
    \label{fig:power}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth,clip]{plots/combined/cost.pdf}
    \caption{Training, Prediction, and Attack Monetary Cost Across Datasets and Hardware}
    \label{fig:cost}
\end{figure}
